Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-12-31 code/analysis.Rmd
boxed legends in plots

plotece1 <- final %>%
  filter(dowel_density != "0000") %>%
  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
  ggplot(aes(x = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, color = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
  geom_point(position = position_dodge(width = .55)) +
  geom_errorbar(width = 0.4, position = position_dodge(width = .55)) +  
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Effective Capture Efficiency", x = expression(paste("Collector Reynolds Number (",Re[c]," )")), color = expression(phi[c])) +
  theme_bw() +
  theme(legend.position = "bottom")

plotece2 <- final %>%
  filter(dowel_density != "0000") %>%
  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
  ggplot(aes(color = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, x = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
  geom_point(position = position_dodge(width = .55)) +
  geom_errorbar(width = 0.4, position = position_dodge(width = .55)) +  
  scale_y_continuous(labels = scales::percent) +
  scale_color_manual(values = c("purple","orange","brown")) +
  labs(y = "Effective Capture Efficiency", color = expression(Re[c]), x = expression(paste("Collector Solid Volume Fraction (",phi[c]," )"))) +
  theme_bw() +
  theme(legend.position = "bottom")

@@

cplot <- c_over_phi %>%
  ggplot(aes(x = phi, y = C, pch = factor(lab, levels = c("This study", "Fauria et al. (2015)")), color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
  geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
  geom_point(size = 2) +
  theme_bw() +
  labs(x = expression(paste("Collector Solid Volume Fraction (", phi[c], " )" )), color = "", pch = "") +
  scale_color_manual(values = c("darkgreen","red")) +
  scale_x_continuous(labels = scales::percent)

>>>>

plotece1 <- final %>%
  filter(dowel_density != "0000") %>%
  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
  ggplot(aes(x = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, color = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
  geom_point(position = position_dodge(width = .55)) +
  geom_errorbar(width = 0.4, position = position_dodge(width = .55)) +  
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Effective Capture Efficiency", x = expression(paste("Collector Reynolds Number (",Re[c]," )")), color = expression(phi[c])) +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.background = element_rect(colour = "black", size = .2))

plotece2 <- final %>%
  filter(dowel_density != "0000") %>%
  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
  ggplot(aes(color = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, x = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
  geom_point(position = position_dodge(width = .55)) +
  geom_errorbar(width = 0.4, position = position_dodge(width = .55)) +  
  scale_y_continuous(labels = scales::percent) +
  scale_color_manual(values = c("purple","orange","brown")) +
  labs(y = "Effective Capture Efficiency", color = expression(Re[c]), x = expression(paste("Collector Solid Volume Fraction (",phi[c]," )"))) +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.background = element_rect(colour = "black", size = .2))

@@

cplot <- c_over_phi %>%
  ggplot(aes(x = phi, y = C, pch = factor(lab, levels = c("This study", "Fauria et al. (2015)")), color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
  geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
  geom_point(size = 2) +
  theme_bw() +
  theme(legend.background = element_rect(colour = "black", size = .2),
        legend.title = element_blank()) +
  labs(x = expression(paste("Collector Solid Volume Fraction (", phi[c], " )" )), color = "", pch = "") +
  scale_color_manual(values = c("darkgreen","red")) +
  scale_x_continuous(labels = scales::percent)
